A Horrocks-type theorem for even orthogonal $K_2$

### 2020-03-30 dl-paper.tex
Fix 11 of 3.5 + small fixes

Let $g = z_\beta(Xf, \xi)$ be a generator of type 1 such that $\alpha - \beta \in \Phi$. By~\cref{Zrels}(2) we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi). \label{eq3-1} \end{equation}
The first and the last factors in the right-hand side of the above equation are generators of type $4$ and $1$, respectively. It is easy to see that the second factor is also a generator of type 1, indeed:
\[ x_{\beta - \alpha} (N_{\beta,-\alpha} \cdot mX^2 f) = z_{\beta'}(Xf', 0)\text{ for } f' = N_{\beta,-\alpha} \cdot mX f\text{ and }\beta' = \beta - \alpha \text{ (clearly, $\alpha + \beta' \in \Phi$).}\]
Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$. Again by~\cref{Zrels}(2)
\begin{equation}
z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi). \label{eq3-2} \end{equation}
It is easy to see that the expression in the right-hand side of~\eqref{eq3-2} is a product of generators of type 4, 1, 2.

Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type 1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}(3) 
\begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \end{equation}
and the latter expression is a product of generators of type $4, 1, 1$.

@@

For the rest of this section $M$ denotes the maximal ideal of $A$.
\begin{df} 
Define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
\[ P_{\alpha}(0) = j_+(\widetilde{P}_{\alpha, M}(0)), \ P_{\alpha}(*) = j_+(\widetilde{P}_{\alpha, M}(*)), \]
where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious embedding.
For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$.

Define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\] \end{df}
It follows immediately from the definition of $S_\alpha(a, -)$ that for $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
\begin{equation} \label{eq:Smult} S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).\end{equation}

It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.

\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g = z_\beta(f, \xi)$ from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for generators of type 3 and 5.
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible in the case of a generator of type 1:
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
Clearly, the expression in the right-hand side is a product of generators of type 5, 2, 1.

@@

\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
Now by~\eqref{eq:Smult} and~\cref{P0_conj} one has
\begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right). \end{multline}

@@

\begin{lemma} \label{SR:sharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right). \] \end{lemma}
\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\eqref{eq:Smult} and~\cref{lem:Tulenbaev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

@@

\begin{lemma} \label{SR:obtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
 belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
\end{lemma}
\begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle a, m \rangle$, $s_1 = \langle \epsilon am', -bc^{-1} \rangle$.
From the definition of $S_\alpha(a, -)$, \cref{lem:Tulenbaev-formula}, \eqref{eq:conj-h-x}, \eqref{eq:h-inv} and~\eqref{eq:dennis-stein} we obtain that
 \begin{multline} \label{eq:SRobtuse-computation}
 S_\alpha\left(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)\right) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
 = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
 = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\tfrac{cmX}{1+am}\right) \cdot s_0 = \\
 = x_{\beta-\alpha}(-b) \cdot x_{-\beta}\left(m'X(1 - \epsilon abm'c^{-1})\right) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right).
\end{multline}
Denote by $h_0$ the product of all factors in the above formula except the first and the last one. It is clear that $h_0$ lies in $P_\alpha(0)$. Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$. The required assertion now follows from \eqref{eq:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
\begin{multline} \nonumber
 x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\
  = x_{\beta - \alpha}(b) \cdot S_\alpha(a, g_0) \cdot x_{\beta-\alpha}(-b) \cdot h_0 \cdot x_{-\alpha}\left(\tfrac{m -\epsilon bm'}{1+am}\right) \in P_\alpha(\tfrac{m -\epsilon bm'}{1+am}). \qedhere
\end{multline}
\end{proof}

@@

\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ holds $p_1 \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
\begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $p_1 = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$. Using~\eqref{eq:Smult} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.

>>>>

Let $g = z_\beta(Xf, \xi)$ be a generator of type 1 such that $\alpha - \beta \in \Phi$. By~\cref{Zrels}\eqref{Z2} we get that \begin{equation} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mX^2f) \cdot z_{\beta}(Xf, \xi). \label{eq3-1} \end{equation}
The first and the last factors in the right-hand side of the above equation are generators of type $4$ and $1$, respectively. It is easy to see that the second factor is also a generator of type 1, indeed:
\[ x_{\beta - \alpha} (N_{\beta,-\alpha} \cdot mX^2 f) = z_{\beta'}(Xf', 0)\text{ for } f' = N_{\beta,-\alpha} \cdot mX f\text{ and }\beta' = \beta - \alpha \text{ (clearly, $\alpha + \beta' \in \Phi$).}\]
Now consider the case when $g = z_\beta(f, X\xi)$ is a generator of type $2$. Again by~\cref{Zrels}\eqref{Z2}
\begin{equation}
z_{\beta}(f, X\xi) ^ {x_{-\alpha}(mX)} =  x_{-\alpha} (- mX^2f\xi ) \cdot x_{\beta-\alpha} (N_{\beta, -\alpha}\cdot mXf) \cdot z_{\beta}(f, X\xi). \label{eq3-2} \end{equation}
It is easy to see that the expression in the right-hand side of~\eqref{eq3-2} is a product of generators of type 4, 1, 2.

Now let $g = z_{\beta}(Xf, \xi)$ be a generator of type 1 in the case $\alpha + \beta \in \Phi$. By~\cref{Zrels}\eqref{Z3}
\begin{equation} \label{eq3-3} z_{\beta}(Xf, \xi) ^ {x_{-\alpha}(mX)} = x_{-\alpha} (mX^2f\xi ) \cdot x_{-\alpha-\beta} (N_{\beta,\alpha}\cdot mX^2f\xi^2) \cdot z_{\beta}(Xf, \xi), \end{equation}
and the latter expression is a product of generators of type $4, 1, 1$.

@@

For the rest of this section $M$ denotes the maximal ideal of $A$.
\begin{df} 
We define the following two subgroups of $\overline{\St}(\Phi, R, M[X, X^{-1}])$:
\[ P_{\alpha}(0) = j_+(\widetilde{P}_{\alpha, M}(0)), \ P_{\alpha}(*) = j_+(\widetilde{P}_{\alpha, M}(*)), \]
where $j_+ \colon \overline{\St}(\Phi, A[X], M[X]) \to \overline{\St}(\Phi, R, M[X, X^{-1}]$ is the obvious homomorphism.
For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.

From~\cref{P0_normal} it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows to define the map $S_\alpha(a, -) \colon P_\alpha(*) \to \St(\Phi, A[X, X^{-1}])$ on each coset $P_\alpha(m)$, $m \in M$ via the following formula:
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}.\] \end{df}

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
\end{lemma} \begin{proof} Since $g_2\in P_\alpha(m')$ for some $m' \in M$, we have that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$:
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) \cdot g_1 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) \cdot g_2 \cdot x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \{X, (1+am)(1 + \tfrac{am'}{1+am})\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}
It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} 
We need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator $g$ from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for generators of type 3 and 5.
First of all, consider the case $\alpha + \beta \in \Phi$, which is only possible in the case of a generator of type 1:
\begin{equation}\label{eq:Zconj1} z_{\beta}(Xf, \xi) ^ {x_{\alpha}(aX^{-1})} = x_{\alpha} (- af\xi) \cdot x_{\alpha+\beta} (N_{\beta, \alpha}\cdot af) \cdot z_{\beta}(Xf, \xi). \end{equation}
Clearly, the expression in the right-hand side is a product of generators of type 5, 2, 1.

@@

\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
Now by~\cref{lem:Smult} and~\cref{P0_conj} one has
\begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right). \end{multline}

@@

\begin{lemma} \label{SR:sharp} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a \in A$ holds \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot am') \in P_\beta\left(\tfrac{m'}{1 + am}\right). \] \end{lemma}
\begin{proof} By~\cref{K-a-b} $g$ can be presented as $ g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$, therefore from~\cref{lem:Smult} and~\cref{lem:Tulenbaev-formula} we obtain that \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\tfrac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\tfrac{N_{\alpha, -\beta} \cdot am'}{1+am}\right) = \\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot \langle a, m \rangle \cdot  x_{-\beta}\left(\tfrac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot am'\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

@@

\begin{lemma} \label{SR:obtuse} For $g \in K(A[X], M[X]) \cap P_\alpha(m) \cap P_\beta(m')$ and $a, b\in A$ the element \[ x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}((1 + \epsilon abm')^{-1})\cdot x_{\beta - \alpha}(-b(1 + \epsilon abm')) \]
 belongs to $P_\alpha\left(\tfrac{m - \epsilon bm'}{1+am}\right)$, where $\epsilon = N_{\alpha, -\beta}$.
\end{lemma}
\begin{proof} Set $c = 1 + \epsilon a b m'$, $s_0 = \langle a, m \rangle$, $s_1 = \langle \epsilon am', -bc^{-1} \rangle$.
From the definition of $S_\alpha(a, -)$, \cref{lem:Tulenbaev-formula}, \eqref{eq:conj-h-x}, \eqref{eq:h-inv} and~\eqref{eq:dennis-stein} we obtain that
 \begin{multline} \label{eq:SRobtuse-computation}
 S_\alpha\left(a, x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)\right) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta-\alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\ 
 = S_\alpha(a, x_{-\beta}(m'X)) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_\alpha^{-1} (1 + am) \cdot h_{\beta - \alpha}(c^{-1}) \cdot x_{\beta - \alpha}(-bc) = \\
 = x_{-\beta}(m'X) \cdot x_{\alpha - \beta}(\epsilon am') \cdot x_{\beta - \alpha}(-bc^{-1}) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 = x_{-\beta}(m'X) \cdot x_{\beta - \alpha}(-b) \cdot s_1 \cdot h_{\alpha-\beta}(c^{-1}) \cdot x_{\alpha-\beta}\left(\epsilon acm'\right) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot s_0 \cdot h_{\beta - \alpha}(c^{-1}) = \\
 =  x_{\beta - \alpha}(-b) \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(-\epsilon bm'X) \cdot s_1 \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot x_{-\alpha}\left(\tfrac{cmX}{1+am}\right) \cdot s_0 = \\
 = x_{\beta-\alpha}(-b) \cdot x_{-\beta}\left(m'X(1 - \epsilon abm'c^{-1})\right) \cdot x_{\alpha-\beta}(\epsilon ac^{-1}m') \cdot s_1 \cdot s_0 \cdot x_{-\alpha}\left(-\epsilon bm' X + \tfrac{cmX}{1+am}\right).
\end{multline}
Denote by $h_0$ the product of all factors in the above formula except the first and the last one. It is clear that $h_0$ lies in $P_\alpha(0)$. Using~\cref{K-a-b} we can decompose $g = g_0 \cdot x_{-\beta}(m'X) \cdot x_{-\alpha}(mX)$ for some $g_0 \in K(\alpha, \beta)$. The required assertion now follows from \cref{lem:Smult}, \eqref{eq:SRobtuse-computation} and the preceding lemma:
\begin{multline} \nonumber
 x_{\beta - \alpha}(b) \cdot S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am)\cdot h_{\beta - \alpha}(c^{-1})\cdot x_{\beta - \alpha}(-bc) = \\
  = x_{\beta - \alpha}(b) \cdot S_\alpha(a, g_0) \cdot x_{\beta-\alpha}(-b) \cdot h_0 \cdot x_{-\alpha}\left(\tfrac{m -\epsilon bm'}{1+am}\right) \in P_\alpha(\tfrac{m -\epsilon bm'}{1+am}). \qedhere
\end{multline}
\end{proof}

@@

\begin{lemma}\label{lem:action} For any $[p, h, u]\in \overline{V}_T$ and any $p_1 \in \overline{G}^{\geq 0}_M$ holds $p_1 \cdot [p, h, u] = [p_1p, h, u]$. \end{lemma}
\begin{proof} First of all, notice that the assertion of the lemma can be verified directly in the case $p_1 = z_\alpha(f, a)$ for all $a\in A$, $f\in M[X]$. Using~\cref{lem:Smult} and the fact that $x_\beta(X^2f) \in P_\alpha(0)$ for all $\beta \in \Phi$ it is not hard to show that the assertion also holds for $p_1 = z_\alpha(X^2f, aX^{-1})$.
